Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-10-31 text/paper/paper2.tex
changes result section

41 native speakers of German took part in our study, none of which had
any prior exposure to logic or formal semantics. We excluded 3
subjects due to insufficient performance on controls ($\le 50\%$
correct answers).

@@

Performance on basic control conditions was high (92\% correct
responses on average), indicating that subjects understood the task,
giving truth-value judgements at the ``right'' moment in a sequence
without being influenced in general by inessential features of the
picture material or showing general response biases.

@@

>>>>

Forty native speakers of German took part in our study, none of which had
any prior exposure to logic or formal semantics. We excluded three
subjects due to insufficient performance on controls ($\le 50\%$
correct answers).

@@

\paragraph{Target conditions and positional controls}
Performance on positional controls was high (92\% correct
responses on average), indicating that subjects understood the task,
giving truth-value judgements at the ``right'' moment in a sequence
without being influenced in general by inessential features of the
picture material or showing general response biases.

@@

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
\ref{Fig:LC_judgments}. Judgments were coded as \ec, \lc if they were as expected
under one of these readings, and "other" if they were not. The distributions 
of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}

\begin{figure}
\includegraphics[width=\textwidth]{../pictures/graph_ec.pdf}
\caption{Judgments for prefence-related controls (EC sequence). Relative frequencies
of {\it yes/no} judgments is plotted against the position within the
trial. Each {\it EC sequences} consisted of five pictures, in which the
critical positions for a reading were the third position ("false" corresponded
to an \ec reading) and the fifth position ("true" corresponded to an \lc reading)}
\label{Fig:EC_judgments}
\end{figure}

%\clearpage

\begin{figure}
\includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
\caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
of {\it yes/no} judgments is plotted against the position within the
trial. Each {\it LC sequences} consisted of seven pictures, in which the
critical positions for a reading were the third position ("true" corresponded
to an \lc reading) and the sixth position ("false" corresponded to an \ec reading)}
\label{Fig:LC_judgments}.
\end{figure}

\begin{figure}

\includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
